Explore Vegetation Data

### 2016-02-15 explore_veg_data.Rmd
Update wide formatting data code.

```{r group alt dbh to plot and year}
alt_species
alt_species$Dead[alt_species$Dead==0] <- "Alive"
alt_species$Dead[alt_species$Dead==1] <- "Dead"
alt_species <- rename(alt_species, status = Dead, plotid = PlotID, species = Species)
alt_dbh_plot <- alt_species %>% 
      group_by(plotid, species, status, year) %>% 
      summarise(tot_dbh = sum(dbh, na.rm = T), avg_dbh = mean(dbh, na.rm = T),
                tot_ba_m2 = sum(pi*dbh^2/40000, na.rm = T),
                avg_ba_m2 = mean(pi*dbh^2/40000, na.rm = T),
                abundance = length(dbh))
write.csv(alt_dbh_plot, "analysis/data/alt-dbh-plot.csv", row.names = F)
```

@@

```{r make wide format species abundance}
alt_species$PlotID <- tolower(alt_species$PlotID)
unique(alt_species$Species)
alt_species$Species[alt_species$Species=="arcto sp."] <- "arcto"
alt_species$Species[alt_species$Species=="prunus sp."] <- "prunus"
alt_species$Species[alt_species$Species=="unknown sp. 1"] <- "unk1"
alt_species$Species[alt_species$Species=="quercus sp."] <- "qusp"
alt_species

unique(alt_sp_2014_live$Species)
alt_sp_2014_live$Species[alt_sp_2014_live$Species=="arcto sp."] <- "arcto"
alt_sp_2014_live$Species[alt_sp_2014_live$Species=="prunus sp."] <- "prunus"
alt_sp_2014_live$Species[alt_sp_2014_live$Species=="unknown sp. 1"] <- "unk1"
alt_sp_2014_live$Species[alt_sp_2014_live$Species=="quercus sp."] <- "qusp"

unique(alt_sp_2005_live$Species)
alt_sp_2005_live$Species[alt_sp_2005_live$Species=="quercus sp."] <- "qusp"
alt_sp_2005_live$Species[alt_sp_2005_live$Species=="arcto sp."] <- "arcto"
alt_sp_2005_live$Species[alt_sp_2005_live$Species=="prunus sp."] <- "prunus"

>>>>

```{r group alt species dbh to plot and year}
alt_species
alt_species$Dead[alt_species$Dead==0] <- "Alive"
alt_species$Dead[alt_species$Dead==1] <- "Dead"
alt_species <- rename(alt_species, status = Dead, plotid = PlotID, species = Species)
alt_dbh_plot <- alt_species %>% 
      group_by(plotid, species, status, year) %>% 
      summarise(tot_dbh = sum(dbh, na.rm = T), avg_dbh = mean(dbh, na.rm = T),
                tot_ba_m2 = sum(pi*dbh^2/40000, na.rm = T),
                avg_ba_m2 = mean(pi*dbh^2/40000, na.rm = T),
                abundance = length(dbh))
write.csv(alt_dbh_plot, "analysis/data/alt-dbh-plot.csv", row.names = F)
```

@@

```{r make wide format species abundance}
library(tidyr)
alt_dbh_plot <- read.csv("analysis/data/alt-dbh-plot.csv")
# alt_species$PlotID <- tolower(alt_species$PlotID)
# unique(alt_species$species)
# alt_species$Species[alt_species$Species=="arcto sp."] <- "arcto"
# alt_species$Species[alt_species$Species=="prunus sp."] <- "prunus"
# alt_species$Species[alt_species$Species=="unknown sp. 1"] <- "unk1"
# alt_species$Species[alt_species$Species=="quercus sp."] <- "qusp"
# head(alt_species)

head(alt_dbh_plot)
unique(alt_dbh_plot$species)
alt_dbh_plot.wide <- as.tbl(alt_dbh_plot %>% 
      select(plotid, species, status, year, abundance) %>% 
      spread(species, abundance))

# unique(alt_sp_2014_live$Species)
# alt_sp_2014_live$Species[alt_sp_2014_live$Species=="arcto sp."] <- "arcto"
# alt_sp_2014_live$Species[alt_sp_2014_live$Species=="prunus sp."] <- "prunus"
# alt_sp_2014_live$Species[alt_sp_2014_live$Species=="unknown sp. 1"] <- "unk1"
# alt_sp_2014_live$Species[alt_sp_2014_live$Species=="quercus sp."] <- "qusp"
# 
# unique(alt_sp_2005_live$Species)
# alt_sp_2005_live$Species[alt_sp_2005_live$Species=="quercus sp."] <- "qusp"
# alt_sp_2005_live$Species[alt_sp_2005_live$Species=="arcto sp."] <- "arcto"
# alt_sp_2005_live$Species[alt_sp_2005_live$Species=="prunus sp."] <- "prunus"
